Industrial, large-scale model predictive control with structured neural networks

### 2020-09-05 paper.tex
minor edit.

To gauge the performance of the NNs in 
the validation simulations, computational 
speedups over online QP based MPC, the offline
computational effort required to build the NNs,
and the memory required for the deployment of NNs,  
the following metrics are examined:

>>>>

To gauge the performance of the NNs in 
the validation simulations, the computational 
speedups over online QP based MPC, the offline
computational effort required to build the NNs,
and the memory required for the deployment of NNs,  
the following metrics are examined:
